My title: still thinking

### 2024-04-13 paper/paper.qmd
Updated LLM usage

@@

@@

@@

On average, 39% of users end up rating an anime on their list according to @fig-scoring_fraction. There is a strong positive correlation between scoring fraction and popularity, which is sensible as fans of an anime or any media in general are likely express their opinion on that particular media. Surprisingly there is a positive correlation between scoring fraction and rank. One might expect a normal distribution as people are more likely to voice their opinion on a particularly good or bad piece of work but not so much for average ones. Instead we see a linear relationship scoring fraction and rank.

@@

>>>>

### Score Distribution (is there such thing as too many sections?)

@@

### Rank and Popularity

@@

### Date and Popularity

@@

### Scoring Fraction

On average, 39% of users end up rating an anime on their list according to @fig-scoring_fraction. There is a strong positive correlation between scoring fraction and popularity as seen in @fig-fraction_relationships-1, which is sensible as fans of an anime or any media in general are likely express their opinion on that particular media. Surprisingly in @fig-fraction_relationships-2 there is a positive correlation between scoring fraction and rank. One might expect a normal distribution as people are more likely to voice their opinion on a particularly good or bad piece of work but not so much for average ones. Instead we see a linear relationship scoring fraction and rank.

@@

TODO look at studio and genre
